API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
Slightly better wording
Another e.g. comma

Building on the core interface introduced in the previous section, we now
present advanced API mechanisms for building meta-estimators,
composing complex estimators and selecting models. We also discuss design
choices allowing for an easy use and extension of \sklearn.

@@

Some machine learning algorithms are expressed naturally
as meta-algorithms parametrized on simpler algorithms.
Examples include ensemble methods which
build and combine several simpler models (e.g., decision trees), or multiclass
and multilabel classification schemes which can be used to turn a binary
classifier into a multiclass or multilabel classifier. In \sklearn, such algorithms are
implemented as \textit{meta-estimators}. They take as input an existing base
estimator and use it internally for learning and making predictions.
All meta-estimators implement the regular estimator interface.

>>>>

Building on the core interface introduced in the previous section, we now
present advanced API mechanisms for building meta-estimators,
composing complex estimators and selecting models. We also discuss design
choices allowing for the easy usage and extension of \sklearn.

@@

Some machine learning algorithms are expressed naturally
as meta-algorithms parametrized on simpler algorithms.
Examples include ensemble methods which
build and combine several simpler models (e.g. decision trees), or multiclass
and multilabel classification schemes which can be used to turn a binary
classifier into a multiclass or multilabel classifier. In \sklearn, such algorithms are
implemented as \textit{meta-estimators}. They take as input an existing base
estimator and use it internally for learning and making predictions.
All meta-estimators implement the regular estimator interface.
